Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check section on importance sampling

        \subsubsection{Importance Sampling}
            A problem with the naïve Metropolis-Hastings sampling approach
            described above is that the sampling of position space is done with
            no regard for where we are likely to find a particle. This problem
            can be remedied through \emph{importance sampling}.  It is
            reasonable to assume that the particles we erratically scatter in
            space are prone to movement towards the peaks of the probability
            density as dictated by the wave function. Consider therefore the
            Fokker-Planck equation,
            \begin{align}
                \dpd[]{\Psi_T}{t}
                &=
                D \nabla\cdot
                \left(
                    \nabla
                    - \vf{F}
                \right) \Psi_T,
                \label{eq:fokker_planck}
            \end{align}
            which describes the evolution in time of a probability density
            function. In our case this is the trial wavefunction $\Psi_T$.
            Originaly an equation that models diffusion, we have a diffusion
            term $D$ and the drift force \autoref{eq:drift_force}. In our case
            the diffusion term $D$ is simply $1/2$ from the kinetic energy (in
            natural units).

@@

            Now we need to change the acceptance probability of the metropolis
            algorithm to something that takes the new sampling method into
            account.
            \begin{align}
                q(\vf{r}_{i + 1}, \vf{r}_i)
                &=
                \frac{
                    G(\vf{r}_{i + 1}, \vf{r}_{i}, \delta t)
                    \left|\Psi_T(\vf{r}_{i + 1})\right|^2
                }
                {
                    G(\vf{r}_{i}, \vf{r}_{i + 1}, \delta t)
                    \left|\Psi_T(\vf{r}_{i})\right|^2
                },
            \end{align}
            where $G$ is the Green's function of the Fokker-Planck equation
            given by
            \begin{align}
                G(\vf{r}_{i + 1}, \vf{r}_i, \delta t)
                &=
                \exp\Biggl(
                    -\frac{\bigl[
                        \vf{r}_{i + 1}
                        - \vf{r}_{i}
                        - D\vf{F}(\vf{r}_i)\delta t
                    \bigr]^2}{4D\delta t}
                \Biggr)
                \nonumber \\
                &\qquad
                \times
                \frac{1}{(4\pi D\delta t)^{dN/2}},
            \end{align}
            where $d$ is the dimensionality.

>>>>

        \subsubsection{Importance Sampling}
            A problem with the naïve Metropolis-Hastings sampling approach
            described above is that the sampling of position space is done with
            no regard for where we are likely to find a particle. This problem
            can be remedied through \emph{importance sampling}.  It is
            reasonable to assume that the particles we erratically scatter in
            space are prone to movement towards the peaks of the probability
            density as dictated by the wave function. Consider therefore the
            Fokker-Planck equation,
            \begin{align}
                \dpd[]{\Psi_T}{t}
                &=
                D \nabla\cdot
                \left(
                    \nabla
                    - \vf{F}
                \right) \Psi_T,
                \label{eq:fokker_planck}
            \end{align}
            which describes the evolution in time of a probability density
            function. In our case this is the trial wavefunction
            $\Psi_T$\footnote{The trial wavefunction is not a probability
            density, but the Fokker-Planck equation is robust enough to handle
            the wavefunction as is.}.  Originaly an equation that models
            diffusion, we have a diffusion term $D$ and the drift force
            \autoref{eq:drift_force}. In our case the diffusion term $D$ is
            simply $1/2$ from the kinetic energy (in natural units).

@@

            Now we need to change the ratio computation in the
            Metropolis-Hastings algorithm to something that takes the new
            sampling method into account.
            \begin{align}
                q(\vf{r}_{i + 1}, \vf{r}_i)
                &=
                \frac{
                    G(\vf{r}_{i}, \vf{r}_{i + 1}, \delta t)
                    \left|\Psi_T(\vf{r}_{i + 1})\right|^2
                }
                {
                    G(\vf{r}_{i + 1}, \vf{r}_{i}, \delta t)
                    \left|\Psi_T(\vf{r}_{i})\right|^2
                },
            \end{align}
            where $G$ is the Green's function of the Fokker-Planck equation
            given by
            \begin{align}
                G(\vf{r}_{i}, \vf{r}_{i + 1}, \delta t)
                &=
                \exp\Biggl(
                    -\frac{\bigl[
                        \vf{r}_{i}
                        - \vf{r}_{i + 1}
                        - D\vf{F}(\vf{r}_{i + 1})\delta t
                    \bigr]^2}{4D\delta t}
                \Biggr)
                \nonumber \\
                &\qquad
                \times
                \frac{1}{(4\pi D\delta t)^{dN/2}},
            \end{align}
            where $d$ is the dimensionality. The new ratio, $q$, is still
            subjected to the same ratio test as in the brute force
            Metropolis-Hastings algortihm.
